\Large \bf Compilers Project: PTX Super-optimization

### 2018-05-01 paper/main.tex
pretty print, README, and paper tweaks

The key algorithm behind the super-optimiser \cite{superopt}
is a context-aware graph search with various clever
optimizations that minimize the number of redundant computations.
These optimizations entail keeping the same items pruned:
so if the search finds that a class of programs
can be pruned, it keeps them pruned across all
the relevant restarts and input refinements.

@@

\texttt{pyparsing} is the main library this program rests on.
Assuming just the instructions, the program can read and parse
the most basic arithmetic instructions, handling a few hundred.

@@

The Ocelot project \cite{GPUOcelot} showed that though a project may seem promising,
its maintenance may not exist. Building the project proved to be impossible as the versions
only aligned when the project was built and that astronomical event has passed.
In the future, less time should be spent behind one project, especially if it does not build.

@@

@@

Hacker's delight and other small segments of
straight-line code will likely be the first
victims of super-optimisation to test the
encoding of the PTX ISA.

Most useful benchmarks would arise from the related works aforementioned:
the hiCUDA \cite{hicuda} framework's tests and tests
from the CUDA loop optimiser \cite{CUDASynth} would likely
be the final benchmarks.

>>>>

The key algorithm behind the super-optimiser \cite{superopt}
is a context-aware graph search with various clever
optimizations that minimize the number of redundant computations.
These optimizations entail keeping the same items pruned:
so if the search finds that a class of programs
can be pruned, it keeps them pruned across all
the relevant restarts and input refinements.
Furthermore, the LENS algorithm searches both forward and backward,
using stronger pre-conditions inferred from searching. These
optimizations are discussed as a future direction for this project.

@@

\texttt{pyparsing} is the main library this part rests on.
Assuming just the instructions, the program can read and parse
the most basic arithmetic instructions, handling a few hundred.

@@

The Ocelot project \cite{GPUOcelot} showed that though a project may seem promising,
its maintenance may not exist. Building the project proved to be impossible as the versions
only aligned when the project was built and that astronomical event has passed.
In the future, less time should be spent behind one project, especially if it does not build.
Alternatives, such as \texttt{pyparsing} should have been considered much sooner.

@@

Another theoretical improvement would be finding a
more accurate heuristic or proving the accuracy
of the current one through stronger, more realistic,
benchmarks. Currently the code generator is likely
not robust enough to compete against NVCC.

@@

Hacker's delight and other small segments of
straight-line code will likely be the first
victims of super-optimisation to test the
basic implementation of non-parallel algorithms.

Most useful benchmarks would arise from the related works aforementioned:
the hiCUDA \cite{hicuda} framework's tests and tests
from the CUDA loop optimiser \cite{CUDASynth} would likely
be excellent benchmarks.
